\chapter{The Search for the Enchanted Balls}

Centuries ago, on a planet called Gossameria, there lived animals that roamed carefree over its unspoiled landscape. They lived in harmony with their neighbors and gathered regularly for the purposes of frolicking and celebrating special occasions. In summer, they picnicked near the beaches of lakes which were so clean that all life swimming within it was clearly visible. They played joyfully in vast, grassy fields. It was quite common for the animals of this world to live for thousands of years.

Two cats were members of this community: Katharine (a primarily orange cat with narrow brown stripes) and Jacob (who had black fur on his back that blended into gray around his sides and white near his tummy). They had been best friends for almost three hundred years. They each owned a special enchanted ball and played with them almost every time they met. Katharine's ball was pink with purple stripes; Jacob's was bright green with small yellow circles.

Almost every day they played in a meadow covered with green grass and dotted with yellow, red, and purple wildflowers. When the grass grew too high, several helpful sheep would eat some. The cats were grateful for the sheep’s efforts. Katharine and Jacob found it much easier to play with their enchanted balls when they could see each other, and their balls could roll freely over the ground.

One day as they were playing, they both became momentarily distracted by a large dog wandering nearby. They turned their attention back to their enchanted balls, but to their dismay, they had vanished. Katharine and Jacob frantically searched the field for several hours.

After the sun set, they reluctantly agreed to return to their homes for the night and continue searching tomorrow. They were heartbroken. After arriving home, Katharine and Jacob fell into their beds, all joy and hope drained from their bodies. They cried and meowed until a heavy sleep overtook them.

Soon after, their sleep became disturbed by nightmares and their limbs began to frequently twitch. Hours later, they were awoken by a rooster crowing at the rising sun. They felt as if they hadn't slept at all. Later that morning, Katharine and Jacob met under a weeping willow tree standing near a lakeshore. They peered out over the water, which softly reflected the sunlight. Neither of them appreciated or even noticed the beauty of the scene, nor of the shade and shelter the tree generously provided.

Their tails hung low. Katharine suddenly turned to look at Jacob. As they stood there, Jacob saw that Katharine was thinking hard, and then he observed her tail slowly begin to rise. Katharine declared, “We have to keep searching.” Jacob sadly looked into her eyes. She continued, her voice firm and direct, “It doesn't matter how much time we spend—at any cost, we must find them.”

Hesitantly, Jacob replied, “We looked all over that field, Kat. We covered every square inch. Where else could they be?”

She sidestepped his question and with a wry smile answered, “We'll know that when we find them.”

Jacob appeared dubious but after a few moments he finally agreed. That fateful day, they both completely committed themselves to the search for their enchanted balls. They went back to the meadow and searched it again. They asked the sheep if any of them had seen the balls. They searched around the lakeshore. They looked through nearby fields and hills. They went even further away from their homes and searched through mountain passes and valleys.

Weeks went by. They felt very discouraged, but more determined than ever to recover their beloved toys. They continued searching every place they could think of.

\timesep


Three years after their search began, humans suddenly came to Gossameria for the first time and began colonization. Steamships and airplanes were among the many things the newcomers constructed. Katharine and Jacob took advantage—they were able to steal passage on vehicles that moved over water and through the sky, which allowed them to search previously unreachable areas.

It wasn't until 128 years later they completed searching their entire world. Still, they hadn't found their balls.

It was at that time when the humans began building spaceships. Although a spaceship had originally brought the humans to Gossameria, the planet didn't have the required materials to produce the correct type of fuel. It took over a century for six generations of engineers to finally manufacture a ship that could use the resources available on Gossameria.

Katharine and Jacob curiously watched the construction. They fled in terror the first time they heard a spaceship's engines ignite.

One night, they crept into a large building near the launchpad. They slowly walked near to a group of people. It consisted of mechanics and ground crew flight coordinators. Katharine and Jacob eavesdropped on their conversation. The cats happily learned that spaceships could help them continue their search. They also learned the precise time and date of the next launch.

They anxiously waited seven days. At dawn, they sneaked into a top-secret facility. They sniffed the area and spotted some very large plastic cargo containers. They jumped up and landed inside one. Most of their weight fell against the side and it almost tipped over. They landed on human clothes and blankets. They burrowed under the soft, warm material.

As the dust settled, they both sneezed several times.

After only a few minutes they heard a human walking nearby. They heard a “snap” as a lid was secured over the container.

“Kat, I'm starting to wonder if we're making the best life-choices,” Jacob declared.

“Keep quiet. We'll be all right. Did you sharpen your claws yesterday?”

“Yes. Do you think we'll need to resort to violence?”

“Probably not. I hope not.” Katharine replied in a flat tone that didn't sound convincing or reassuring.

They felt the container being picked up, moved a few feet and set down on a wheeled cart. It was pushed to the launchpad. Soon, someone carried the container into the ship's cargo hold and set it on a high stack of other cargo.

At this point, the cats were frightened and wanted to escape. They knew, however, that it was too late. Based on the activity heard from their surroundings, they would most certainly be spotted if they tried to make a run for it.

About two hours passed. No voices could be heard. They pushed up on the container's lid. It didn't budge. They continued trying for two minutes. They looked around for a tool and found a belt buckle. Jacob was able to wedge open the lid enough to loosen it. They became confident escaping at the last minute—if they felt proceeding would be too risky—would be possible.

Suddenly, the ship's engines came to life. Moments later, the cats felt the pull of gravity throughout their entire bodies. They remorsefully realized it was too late to change their minds. Also terrified, they made sure not to loudly meow or cry. Their tails became very tense. They closed their eyes and breathed heavily... and waited for the horrible experience to be over.

\timesep

After two days, Katharine and Jacob were starving and thirsty. They agreed to start searching for a food and water supply. Jacob opened the lid far enough to get out. After being loosened by the belt buckle, the lid separated easily from the top of the container. They both crawled out and then stretched their bodies and tails as much as possible. They had never been trapped for such a  long time.

Katharine and Jacob sniffed around, whiskers twitching wildly. After several minutes they found a water source and scraps of food left by some crew and passengers (who apparently didn't understand that food is meant to be eaten, not thrown onto the floor). The cats quickly and easily found adequate nutrition.

They desperately needed to use the bathroom before returning to their container. Fortunately, while searching for water, they had stealthily observed the humans using a computer-automated waste recycling system. Katharine and Jacob were able to dispose of that which they would have otherwise buried in sand or dirt. Afterward, they went back to the container and slid the lid back into place. They fell asleep after only a few minutes, and blissful dreams about their enchanted balls began shortly after.

\timesep

After three months of confinement (interspersed with scrounging for food and water), the cats felt the spaceship land. They were in good health but poor spirits. They cheered up considerably when they knew the ship was on the ground and their freedom was imminent.

Jacob whispered, “How long should we wait before getting out?”

“After the human voices and footsteps disappear. We'll watch carefully and try to follow the last one outside.”

They knew how many people had originally boarded the ship—they had figured it out easily during their three months on board. They also knew one had died. A passenger had contracted some disease that wasn't detected before departure. Without proper medical facilities on the ship, “There wasn't anything that could be done,” the Captain was heard saying, with regret and sadness clouding his voice. The passenger was given a respectful funeral, and ejected into space. She was cremated after the gravity from a star drew her in (luckily, that was the custom within her family).

Katharine and Jacob counted the humans as they departed the ship. One of them had a frayed thread hanging from the leg of his uniform. Jacob wanted to chew on it and bat it with his paw, but Katharine held him back. She snapped,  “Jacob, stay focused!”

Katharine counted the humans as they exited the ship. “16... 17... 18... 19. All right, quietly now, let's get behind that tall human and follow him out; he's the last one. When we reach the other side of the doorway, look for cover, then run toward it as fast you can.”

They sneaked near to the human's feet, Katharine on the left, Jacob on the right. The human suddenly stopped, put his arm to his face and sneezed. The cats looked at each other with concern. They had heard humans do this before and knew that sneezes sometimes happened when humans were in proximity to them.

He pulled a handkerchief from his pocket, blew and wiped his nose; then he glanced down and spotted Katharine and Jacob. They looked directly into his eyes but weren't able to sense whether danger was imminent. Jacob looked to Katharine for guidance. Trying to scare the human, she meowed loudly, bared her teeth and emitted a hissing sound. Her efforts were in vain. The human simply turned his head and shouted outside, “Cap'n! We got stowaways!”

He leaned over, hands and long arms coming down toward Jacob. “Run, Jacob!” Katharine commanded, her instincts taking over. Jacob sprinted toward the doorway. Katharine followed him straightaway.

They got past the exit and kept running in a straight line, darting past five humans easily; however, one was standing directly in front of their escape route. It was the ship's captain, and he looked very displeased. He squatted downward to snatch Katharine and Jacob. Katharine directed Jacob, “Veer left! I saw some thick bushes!”

Jacob hadn't seen any but he trusted Katharine enough to do as he was told. He slowed almost to a stop and started to make the turn, but the captain grabbed him by the sides of his stomach and scooped him up. “Well, little fellow, did you think you could get free passage on my ship and then just run away like a scared little kitty-cat?” Jacob squirmed in his grasp, squealed loudly, then looked to his left. He saw a bunch of green raspberry bushes but didn't see Katharine anywhere. \textit{I hope she got away}, thought Jacob.

“Argh!” the captain suddenly cried out, dropping Jacob.

He landed safely on his feet and saw Katharine gripping the captain's right leg with all four paws. Jacob realized she had created a diversion by digging her claws deeply into his calf. The captain bent over to reach for her. At the same moment, she retracted her claws, fell off the captain's leg, and yelled, “Run to the bushes, Jacob!”

He ran as fast as he could. Halfway to the bushes, he looked behind to make sure Katharine was with him. He saw the captain had grabbed her, and she was ferociously attacking his arms with her claws and teeth. Jacob was terrified. He stopped, then started running back so he could help. It wasn't necessary though; Katharine had managed to inflict so much damage on the captain that he couldn't hold her. He dropped her and she started running toward Jacob. "Go!" she screamed.

He saw the captain and some crewmen begin chasing them. He turned back around and ran, just as Katharine ordered. He felt reasonably confident she was no longer in any immediate danger.

He reached the left side of a row of thick bushes, ran behind them, and then zig-zagged through some tall flowers on the other side. He stopped to wait for Katharine. Quite familiar with his smell, she found him easily. They heard the captain and two of his crew members nearby and swiftly approaching. “There, that forest.” Katharine pointed to a large wooded area.

“But there's no cover between here and the tree line! They'll catch us!”

“We can outrun them. Let's go!” Katharine started to sprint towards the trees, not waiting for him to verbalize his agreement. Jacob decided there was no other choice and continued after her.

The pursuers relented after two minutes. The captain shouted after them, “You won't be so lucky if I ever see you again. From now on, I'll make sure there's a dog on every ship to prevent stowaways like you from ever boarding!” He and his crewmen walked back to the ship, feeling angry and humiliated from being outsmarted by the two cats.

\timesep

Katharine and Jacob reached the tree line and entered the forest. After catching their breath and walking for several yards, they stopped at a large pile of oak leaves and crawled on top. They lay down to rest. After a few minutes, Jacob glumly declared, “We'll never be able to get back home.”

“Let's not worry about that now. At least we're safe. We need to stay focused on finding our balls.”

“What makes you think they're even on this world?”

Suddenly, Katharine and Jacob heard paw-steps softly approaching. They looked in the direction of the sound and spotted a hollow log. From the darkness within it appeared a small pair of eyes. They seemed to almost glow. Katharine and Jacob remained cautious, ready to scamper away.

A white Persian cat slowly stepped out from the log. Jacob and Katharine relaxed a little. Though somewhat relieved to see a creature their own size, they remained in a state of heightened anxiety. The unfamiliar cat sat down on his hind legs. He looked directly at them and said, “I understand you are searching for something. In my experience, the only time one can clearly see is when he or she ceases to look for things.”

Katharine and Jacob looked at each other with confusion. Katharine asked, “Who are you?”

“My name is Tobias. And you?”

“I'm Katharine, and this is my friend, Jacob.”

“It is a pleasure to meet you. Welcome to the forest.”

“Thank you,” Jacob replied. “Is this your home?”

“My home is anywhere I am happy and content.” Tobias paused, closed his eyes, took a deep breath and slowly exhaled. “I overheard you speaking about the search for your balls. May I ask why they are so important?”

Katharine replied, “They were enchanted, and our favorite toys.” She went on to chronicle the story of their search; Jacob filled in a few gaps he felt relevant.

They finished relating the tale, and Tobias said, “It is indeed unfortunate that you lost your enchanted balls, but in my opinion, it is even more unfortunate that you've lost so much time looking for them. Lost time is a sad waste of a precious thing that can never again be found.”

Katharine and Jacob became angry and reflexively extended their front claws. Jacob irritably exclaimed, “It wasn't a waste! We just haven't found them yet!”

Katharine replied coldly, “You don't understand. You never played with our balls and so don't realize how wonderful they were.”

“Forgive me. I did not mean any offense, nor did I intend to minimize your efforts or intense grief from the loss.” Tobias paused, closed his eyes, took a deep breath and slowly exhaled. “Have you considered the possibility that your enchanted balls rolled into a lake and became submerged?”

Katharine retracted her claws and replied, “Yes, of course. But Jacob and I don't like water. It's good to drink, but other than that we don't really see any purpose to water.”

Jacob continued, “Most of the time we spent on dry land. Sometimes we stowed away on boats to search other islands and continents, but we didn't really care for the water being on all sides of us. It was really very nerve-wracking.”

“I see,” said Tobias. He paused, closed his eyes, took a deep breath and slowly exhaled.

Katharine looked at him curiously for a moment and asked, “Why do you keep doing that?”

“It relaxes me.”

“Are you nervous?”

“No,” he answered. “Deep breathing is a habit I started a long time ago. It helped me through a very difficult period in my life.”

“What do you mean?” Jacob inquired.

“Many years ago, I had a friend named Brittany. We also owned a pair of enchanted balls. One day when she and I were playing, we lost control of them, watching helplessly as they rolled into a fast-moving river. We ran along the riverbank after them, seeing them floating on top but powerless to do anything about it. The river continued to swiftly carry them further away. It soon became evident that it would be impossible to retrieve them.

“Suddenly, Brittany said, 'I'm going in.' I tried to stop her. As she was about to jump in I shouted after her, 'No, Brittany! It's water! You'll never survive!' She ignored my warning and jumped in.” Tobias paused, closed his eyes, took a deep breath and slowly exhaled.

“I never saw her again. I believe she now rests with the \textit{Divine Felinity}, in the spiritual realm where food is always abundant and cats never gain weight; where water is always cold and refreshing to drink, yet it never touches a cat's fur, and contains no soggy food chunks from the day before; the place where a new toy appears daily, and one's curiosity is always stimulated by some external object possessing a strange new smell. Although she's at peace, I do still miss her.”


“That's awful!”

Jacob looked thoughtful. “I almost lost Katharine during our search when she was captured by a human.”

“I hope you consider yourself fortunate.”

“We do, but we still need to find our balls,” Katharine declared.

Jacob paused, closed his eyes, took a deep breath and slowly exhaled. “No, we don't.”

“Jacob! Of course we do. You don't mean that!”

“I do. Our search nearly cost your life. You mean more to me than any enchanted ball.”

“But Jacob, we agreed—"

“Katharine, you're a good leader, and able to make quick decisions, but take a minute to think of how you'd feel if you lost me.”

Katharine didn't need a minute. After a few seconds, she knew her friend was correct.

Tobias said, “Come, my friends. This forest has much to offer. There is ample food, many new things to smell, and it offers an abundance of corners and things under which you may hide, if you feel such a need. I believe you will find peace and contentment if you decide to stay.”

“Thank you, Tobias.”

He acknowledged with a single nod. “Some even claim this forest is enchanted. You might be surprised at how quickly you forget about your balls.”

Indeed, Jacob looked around and spotted some low-hanging vines swaying in the breeze. He joyfully exclaimed, “\textit{Those} look interesting!”