\chapter{James's Love}

James loved his family and friends. He loved God and his church, and he loved the outdoors, the sunlight, and all the wonders of Creation. Like all people, however, the love in James's heart was sometimes covered by—or mixed in with— other feelings, some which were unpleasant and had the potential to be harmful to himself or others.

He had recently bought a new car. It was the best one he'd ever owned; it was comfortable, stylish, and fuel efficient. It was reliable and got him to work on time every day. It carried him to meet his friends, and visit his beloved family. James used his car every day and became very accustomed and attached to it. He relied on it to be there for him when needed. He loved the car, and sometimes even felt the car loved him.

On Thanksgiving, he drove to meet his family to join them for the holiday. James always greatly enjoyed spending time with them. Though he felt sad when saying goodbye, he always left with new memories to cherish when they were apart.

James carefully drove onto his parents' driveway and parked his car. He got out, locked the doors, and walked up to house. He rang the doorbell, and it only took a few seconds for Philip (his father) to open the door. Philip waved him in and hugged him warmly. James looked around and saw his brother and sister, standing next to their spouses with James's nephews and nieces. They all excitedly welcomed him home.

James looked over the room trying to find Joyce, his mother. “Where's mom?” James asked.

His father replied, “She went to the grocery store to pick up a few things for dinner tomorrow. She should be back in an hour.”

Half of that hour passed quickly with laughter, conversation, and play-time with the children. Then James decided to walk to the corner store to buy chewing gum for himself, and a houseplant for his mother. He reached the store in only a few minutes. After buying a pack of peppermint gum and a beautiful peace lily, he started his short walk home. A chance encounter with friends whom he hadn't seen for a while delayed him by fifteen minutes. After exchanging news and updated contact information, James continued walking home.

As he neared his parents' driveway, he saw his mother's car parked behind his. He was glad she was home—he was anxious to see her and give her the lily.

His mood quickly changed when he spotted the rear bumper on his car. It was scratched, pushed in an inch, and some minor damage to the surrounding area. As he got closer, he noticed on his mother's car that her front bumper had similar damage. He knew then that she was responsible. He instantly, almost reflexively, became angry at her carelessness. James violently threw the peace lily at the ground. The pot cracked, spilling dirt and the flower fell apart. A sudden, strong gust of wind scattered its remnants across the lawn.

Many unpleasant thoughts went through James's mind, and undesirable emotions buried his love as they stabbed into his heart. He marched inside and slammed the door. He looked into the living room and saw his mother on the couch crying. James's sister, Ruth, was sitting beside her, trying to comfort her. As Ruth's eyes met his, her expression silently demanded that he should let their mother know that everything was okay. Without acknowledgment, he stomped off into the kitchen and yanked a bottle of beer from the refrigerator.

James's father followed him into the kitchen. Philip saw that his son's face was red with anger, and his body as tense and hard as a black diamond. He calmly poured himself some water, then spoke softly. “Your mother is really upset that she hit your car. She knows how much it means to you. She was very distracted when she got home, looking forward to spending time with everyone. She's been pretty lonely the last few years, now that everyone's moved out on their own.”

James looked at his father in silence. It was obvious to Philip that his words had an effect—he noticed James had softened. After a few seconds, James set down his beer, of which he'd only drunk a sip. He reached into the refrigerator and pulled out a gallon of orange juice. He grabbed a glass from the cupboard. After filling it, James took a deep breath, walked into the living room, and offered it to his mother. Joyce had always loved orange juice. His earliest childhood memories consisted of her drinking a glass every morning, after she'd served him breakfast.

She accepted the juice. “I'm sorry,” Joyce said timidly.

James shook his head. “Mom, you don't have anything to apologize for. You didn't do it on purpose.” He pulled a tissue from a dispenser, dried the tears from her lovely face, and continued. “It was me who chose to lose my temper. I'm the one who should be apologizing. I'm so sorry, Mom... I got confused about what I loved the most.”

She set her orange juice on the coffee table, stood up and gave James a hug and kiss on the cheek. As they embraced each other, Joyce said happily, “It seems we'll have a new memory to treasure. Happy Thanksgiving, James. I love you, too.”