\chapter{The Money Trees}

There was once a mighty kingdom peacefully ruled by a benevolent king and queen. In financial terms, the kingdom's citizens were much like our own: some were rich, some were poor, some fell comfortably into the middle, and many more fell wretchedly below everyone else.

The king's son, Prince Cameron, was rich. He was highly educated, but sometimes didn't utilize his skills and talents. He spent most of his time gambling, partying, and neglecting lessons that would teach him how to be a good ruler.

A peasant named Johann worked on the king's farm. He was hard-working, honest, and always took pride in his work. He had a wife and five children to support, and therefore was poor. He and his family lived in a small two-bedroom house near the castle. They could view the castle through a small broken window, and often they spoke of its beauty and  marveled at its majestic appearance.

Johann had become friends with a peddler named Elijah, who resided about four kilometers beyond the border of the kingdom. He was a pleasant fellow and was always greeted with friendly smiles when he came to the kingdom to peddle his reasonably-priced items. Elijah also brought news to the citizens about noteworthy developments occurring throughout the region. Elijah and Johann met with each other frequently. Often, their days were highlighted by stimulating and friendly conversation.

Johann, walking casually to meet Elijah one afternoon, found a penny lying on the wet, muddy path. He looked in all directions in an attempt to  spot the owner, but he saw no one nearby. He decided to keep the penny for himself, and proceed to the center of town. He joined Elijah there, and after they discussed the weather, Elijah gave Johann news regarding a new castle being constructed about 10 kilometers to the west. Johann was a very curious man, and therefore barraged Elijah with questions about the castle. Elijah was happy to satisfy his curiosity and patiently answered all his questions. Afterward, they parted company. Johann didn't buy anything from Elijah that day. He was aware of Johann's weak financial situation and wasn't bothered by the lack of a sale. The two simply enjoyed each others' friendship and company.

After arriving home, Johann decided to bury the penny he'd found. He had recently bought food for his family; they therefore had enough to sustain them for the near future. At this time, rather than rushing to spend his newly-found penny, he decided the wiser course of action would be to save it for the time when it would be most useful.

After burying the penny in his backyard, he said a prayer to Plutus, the god of wealth and good luck. Johann remembered to thank him for his generosity. He then went inside to greet his family and share the evening meal with them.

The next morning, Johann arose from bed and proceeded to the kitchen for coffee. He glanced out the window to admire the beautiful castle. Instead of the castle, however, he saw a tree. Being a farmer and an accomplished gardener, Johann knew trees didn't grow overnight. He was very puzzled by the sight of it. Postponing his coffee, he went outside to investigate. He approached the tree with intense curiosity and when he reached it, plucked a leaf from a low-hanging branch. The leaf instantly transformed into a silver coin. Even more astounding is that a new leaf immediately grew back in place of the one he removed. He pulled off the new leaf, and it too transformed into a silver coin. Johann rushed back inside, woke his wife, and excitedly told her about their new tree. It made them very happy to know they no longer had any reason to worry about money. Their nine-year-old son, Stephen, had been sick and they anticipated the likelihood that expensive medical services would soon be required to treat him. Johann then departed for his job at the king's garden.

After work that day, Johann joined Elijah at the center of town. Elijah was intrigued at the prospect of someone else having news for a change.

“You buried the penny because you believed saving it was more important than spending it?”

“That's right. I buried the penny and prayed to Plutus and gave him thanks. This morning I discovered the penny had sprouted overnight into a money tree.”

“You can't be serious. How's that possible?”

Johann showed Elijah the two silver coins. Elijah had heard stories about money trees during his travels--and when he was a child his parents often complained about not having one—but he had never seen anyone produce money from a tree before.

“Johann, that's amazing! I have a few pennies at home. I think I'll bury one tonight and hope my soil is as good as yours.” The men both laughed and went on their way. Elijah rushed home to bury a penny, and Johann went home to bury his two silver coins--to save them for the time when they would be most useful.

After Elijah arrived home and finished burying his penny, he said a prayer to Plutus and thanked him for his life as a peddler--a life that offered financial security and gave him many opportunities to meet and talk with the good people of the land.

The next morning Elijah went outside to see if he had a new money tree. Indeed he did. He plucked a leaf from the tree and it transformed into a silver coin. A bright green leaf fully sprouted from where he had plucked the first leaf. He eagerly pulled off another leaf, and it too transformed into a silver coin. A leaf immediately regrew to replace the one that was removed. Elijah again thanked Plutus and headed to the kingdom for the day's work.

Meanwhile, Prince Cameron heard rumors about the money trees and approached Johann to inquire further. Johann told him truthfully what happened and included all the details necessary to grow a money tree. Johann's account was confirmed when the prince ran into Elijah later that day and received the same information. The prince decided he would like to have a money tree of his own. All he needed was one penny. He and his family were so rich that he didn't have any pennies. However, he found a dirty and disgusting peasant and was able to exchange one of his gold coins for a shiny new penny. Prince Cameron went home to his father's castle, and proceeded to do everything Johann and Elijah had done.

The next morning, he had a money tree. He plucked 2000 leaves from the tree, put them into  20 bags, and hired 10 worthless peasants to carry them. Later that evening, Prince Cameron met with his friends and they entertained themselves late into the night by playing poker. He lost all his silver coins placing careless wagers, but his friends didn't mind, and neither did he. He knew that his tree was an excellent source of short-term financial growth, and would be able to regain his losses simply by pulling off more leaves.

The following day, the prince used the money from his tree to buy the castle being built in the west. He hired more workers to expedite its construction. When it was completed, he hired many filthy peasants to keep it clean and work the land surrounding it. He hired many servants to clean his bedroom--all of whom were female--but always fired them the next morning, before they even had a chance to eat breakfast.

While Prince Cameron was enjoying his seemingly endless supply of silver coins, Elijah had used his newfound wealth to expand his inventory. He realized his money tree would provide enough silver if he chose to retire, but he still enjoyed many aspects of his work, so decided to continue peddling. He and Johann still met everyday. Sometimes they'd discuss religion. Both men feared the vengeful wrath of the gods and knew not to speak ill of them. Therefore, they generally kept those discussions short and only spoke of the beautiful and wondrous things the gods created.

Sometimes they discussed politics, but those conversations yielded very few new ideas. They both agreed the king and queen were wise rulers who did their best to ensure justice for all citizens, regardless of their financial status. They agreed more jobs were needed but disagreed on methods of stimulating job growth. They agreed politicians were powerless to control the weather but would do so if they could.

“Funny you should mention the weather,” Elijah began saying. “It seems like we've been longer than usual without rain.”

“Yes, I think you're right,” Johann replied. “I hope it's not a pattern that continues. Stephen gets very thirsty. Doctor Redmond said he needs to drink a lot of water, so I hope we aren't headed for a drought. If water can't be found, I wouldn't be able to buy any no matter how much silver my tree produces.”

“He's not doing any better?”

“He's stable, but there's been no significant improvement within the last two months. My wife and I look forward to him smiling again with healthy cheeks.”

“Tell him I said hi. I'll stop by to visit him tomorrow.”

“He'd like that. Stephen says you're his favorite peddler. All the toys I give him--the ones I buy from you--he keeps near his bed. They're his favorite.”

“That's nice.” Elijah smiled, and then reached into his cart and grabbed a new toy; a stick with a wooden wheel attached using a small pin. Elijah placed his finger on the edge of the wheel and spun it. “You give this to him. It's a present, free of charge.”

“Thank you, Elijah. It's very intricate; he likes these technological gadgets. I have to go now. I wish you a good evening and safe journey home.”

“To you as well, Johann.”

And the two men each departed for their respective homes.

As the two men feared, three weeks passed with very little rain. Although everyone was well-aware of the weather, the king decided to officially proclaim that a drought had come to the land. He decreed a policy of water conservation, which was enforced by employees of the kingdom's Department of Necessary Liquids.

Water was still scarce, however, and Stephen's sickness became worse. Johann bought all the water he could with silver coins from his money tree, but soon, it became so precious that 100 silver coins couldn't purchase even an ounce. Eventually Stephen became so sick Doctor Redmond decided to dispatch eight messengers. They were sent to search the region far outside the kingdom's borders for physicians even more skilled than he. Johann gave 250 silver coins to each messenger. Fortunately, he had been burying coins in his backyard every day since his money tree first sprouted. Because of the scarcity of rain, it had withered and died (two weeks before the king declared drought conditions). The money trees belonging to Prince Cameron and Elijah had also shrunk and turned to dust. However, every day while Johann's tree was alive, he had buried 100 coins in his backyard, had his morning coffee, and left to work in the king's garden. Like  Elijah, Johann had continued working simply because he enjoyed it.

As Johann waited for the messengers to return, he, his wife, and their four other children sat near Stephen's bedside. Elijah visited almost every day, bringing a new toy for Stephen each time. Stephen, however, was too weak to play with them, and they piled up in a corner. Johann and his family prayed to all their gods, and even to the new one about whom they'd recently heard rumors; the one who had sent His Son to Earth to save mankind.

Meanwhile, back at the prince's castle, the servants walked out after he ran out of money and couldn't pay them. The food stores now empty, and without any income or desire for honest employment, he had to move back into the king's castle. His mother, the queen, welcomed her son home with open arms, a kiss on the cheek, and a hot meal. Afterward, she sent him up to the east guard tower, where the king was with the general of the kingdom's army, discussing new security policies. His father was not nearly as forgiving as the queen. 	“When you stop relying on money trees as your sole source of income, and quit gambling, you can have one of the royal bedrooms upstairs. Until then, you can sleep in the coat room next to the bathroom downstairs. And another thing—“ the king stopped speaking when he suddenly spotted eight riders on horseback approach the east kingdom gate, each with a passenger accompanying him. “An attack? A scouting party?”

“No, my Lord,” answered the general. By the number, I judge them to be the messengers and physicians your gardener has hired.”

“Ah, yes,” the king replied calmly. “I do hope they can help poor Stephen. Johann has been such a loyal and dedicated servant; I'd hate for any ill fate to befall a member of his family. I do hope those physicians have the knowledge of the gods to cure the young lad. General, make sure those physicians and messengers have an armed escort while they're here. Pass a message to the cook, and be sure they get a full meal, and a comfortable place to sleep for the night. If the physicians require anything to help treat Stephen, your lieutenants should notify me immediately.”

“Yes, Sir!” The general left to delegate the tasks and ensure the king's orders were fulfilled.

At that moment, the king heard something strike his crown. “What was that?” There was suddenly another strike, but this time, on his nose. He touched it with a finger, and it felt moist. “Thank the creators, they have blessed us with rain!” Within a few minutes, enough rain had fallen to ensure that every square centimeter of dry land in the region would soon be amply saturated with water. “Bring out the water barrels,” the king ordered. “Save what you can; we don't know how long this rain will continue.”

To the delight of people everywhere, it rained continuously for three days and three nights. During that time, eight physicians met under a large green tent hastily erected by employees of the kingdoms Department of Cloth Shelters. Inside, accommodations had been set up for the medical specialists: a large table, chairs, writing tools, and paper. Serfs perpetually walked through to make sure everyone had fresh coffee. The tent was located in proximity to Johann's house. The specialists worked without rest, exchanging ideas and combining their knowledge. Finally they devised a treatment for Stephen; they unanimously agreed it was the best course of action and proceeded to administer it.

Within two days, Stephen's health improved only a little. After five more days, however, Stephen was on his feet again, playing with Elijah's toys. Johann paid them all an extra 500 gold coins and they returned to their respective countries.

Two weeks later, Johann went into town to meet Elijah. His peddling cart was fully stocked with a variety of interesting items, but he had no extra silver coins. “I'm just glad I have a full inventory.”

“I heard Prince Cameron isn't doing very well. He's got some new disease that even those eight specialists can't cure.”

“I heard the same. Well, maybe praying will help.”

The two men talked for a while, then Johann returned home. He opened the front door and saw Stephen at the kitchen table, eating a large meal. Stephen looked up, and smiled at his father. Johann walked to the backyard, and found the penny he had buried. He went back in and gave it to Stephen, and told him, “Now do not squander this penny. I don't have any silver coins left, so we may need that penny one day. We shouldn't need it for quite a while though; the king gave me a generous raise in pay.” He hugged Stephen, and then went to spend time with his wife. He walked in their bedroom and saw her knitting baby clothes. “Our youngest is five years old. Who are you knitting the baby clothes for, dear?” Instead of answering, she set down her knitting accessories and walked over to Johann. She looked him in the eyes, and gently placed his hand on her belly. They both smiled and then wrapped their arms lovingly around each other. They filled two glasses full of water, said a prayer requesting good health and financial stability for their family, and then went to bed.