\chapter{The Problematic 6000}

In the year 5999, humans had found solutions for almost every problem. It was a peaceful era in our future that was hated by all who enjoyed war. With no challenges, many actually believed life was too easy.

Professor Zinkerton was a scientist and inventor working on the one remaining problem: being able to invent good excuses for doing things one would rather not do. For twenty-three years he had worked tirelessly to ensure people would have the ability to conjure bullet-proof excuses for any situation. Finally, on January 1st of the year 6000, he finished his masterpiece.

“Nathan, come here, I want you!” Professor Zinkerton shouted to his assistant, who was in an adjoining room. Nathan rushed to the Professor's aid.

“Is there something I can do for you, Professor?”

“I'd like some orange juice.”

“You don't pay me for that. Is there anything else you need done?”

Instead of answering, the Professor asked, “What is it you're working on?”

“I'm filing my taxes online.”

“Is filing taxes something you have a great desire to accomplish?”

“No, but I can't think of any good excuses to get out of it.”

“Think no further, my young and impressionable assistant. I have completed my life's work. I call it the Problematic 6000.”

“I must have missed the memo. I've been too busy doing grunt work to have knowledge of your reality. What does it do?”

“It creates problems.”

“That's your life's work? It sounds like a really bad idea.”

“Not at all. It only creates problems when there's a desire for them. If one has an unpleasant task that needs to be done, this machine has the ability to create a valid excuse to avoid it. No longer must people be fated to provide weak or lame excuses.”

“It still seems like a bad idea, Professor.”

“You think in such three-dimensional terms, my loyal minion. I will show you.” Professor Zinkerton leaned over the machine, made some adjustments, then pressed a button marked execute. Suddenly, an explosion could be heard from the room that Nathan had been in working on his taxes. Nathan looked into the room and saw his computer had prematurely exploded.

“What the heck was that?”

The Professor replied, “Now you have an excuse not to do your taxes, my inquisitive companion.”

“No, I don't. I can just drive to the library to get the necessary forms.”

“Ah, yes, of course.” Zinkerton leaned over the Problematic 6000, then pressed the execute button. An explosion was heard from outside, and Nathan ran to check. He came back, madder than an irradiated spider. “My car's on fire!”

“You can thank me later.”

“Thank you? Why, right after I get my next twenty-eight paychecks in forty-eight months, I'll wrap that machine around your neck! I still don't have a good excuse for not filing my taxes. The library is only six blocks away. I'll walk there and get the forms.”

“You're correct, of course, my resourceful young apprentice. That isn't a problem at all. Allow me to make it one.”

Zinkerton again pressed the execute button. Nothing happened.

“Thank God. I'm leaving for the library now.” Nathan took one step, but fell down, his face hitting the soft cushion of a chair. Zinkerton checked the display on the Problematic 6000, which read “Disruption of brain and fine motor control completed in .001 second. Have a nice day.”

Zinkerton gleefully said, “You see? Now you have a good, solid excuse not to file your taxes.”

“I have to use the bathroom.”

“Do you truly want to use the bathroom, or is it a task you'd rather put off?”

“I want, I want!”

“Very well.” Professor Zinkerton sighed and reluctantly pressed the off button on the machine.

After Nathan had returned from the bathroom, Professor Zinkerton explained more of the machine's features. “As you are already astutely aware, this machine can create problems for anybody, not just the owner. It therefore can act as a revenge machine. I'm considering marketing a copy of the Problematic and calling its duplicate the Revenge-O-matic 6000.”

“What an original name.” Nathan acknowledged sarcastically. “I'm astonished at your creativity.”

“My mother always said I was gifted.” Zinkerton turned his head toward an adjoining room and yelled, “Mom, am I not gifted beyond your wildest dreams?”

A woman's voice answered back, “Yes. You're my special little boy!”

“I thought your mom was going to move out.”

“I'm her only child. She says she prefers to keep me near to her heart.”

“I don't think it's healthy.”

“Hmmm... my sister said the same thing once.”

“You just said that you were an only child.”

“I'm my mother's favorite.”

“That's not the same thing.”

“It doesn't really matter. Now pay close attention as I teach you how this machine works. You may one day be as brilliant as I.”

Nathan considered his options carefully, and began to relish the idea that some day, or in an hour, he might use the Problematic 6000 against Professor Zinkerton. He smiled at the Professor, and appeared to be much more interested in the machine. “So how does it work?”

“It connects to a person's brain by using dust particles in the air as a conductor. Then using a power source I obtained through illegal means, an electromagnetic field is generated through an integrated circuit I invented--I created the schematic based on a dream I had one night after I had passed out from drinking.”

“The chip decides on the best solution, then makes it a reality. It can get tricky though, because the chip that determines the method of delivery is one-of-a-kind. If it fails before I manufacture another, we are all doomed.”

“Doomed?”

“Yes... doomed.”

“What do you mean \textit{doomed}?”

“I often believe it is preferable not to worry about your final fate until the time comes.”

“What does that mean?”

“Doom is doom. How much more clear can I make it?”

“Do you mean the complete annihilation of the universe?”

“No... only the left side.”

“The left side?”

Professor Zinkerton's cheeks turned red. “This line of questioning makes me uncomfortable. Shall I continue teaching you about this machine?”

“No.” Nathan insisted, “I think first you should manufacture a backup chip to prevent our complete and utter destruction. Protecting the left side of the universe recently jumped to the top of my priority list. Are we, by any chance, in the left side, or the right side?”

“By chance, yes, we occupy that certain space to which you are addressing a concern regarding your ultimate fate.”

Nathan sighed, then suggested, “How about if I help you make that backup chip now?”

“The materials are on back-order. They'll arrive... hopefully before we meet our doom.” Professor Zinkerton laughed heartily, feeling brilliant, and very amused at his own joke.

Nathan sighed again. “Okay, Professor. Teach me of your wonderful machine.”

“This button sets the target individual. Normally you'd keep it on yourself, especially if you need an excuse quickly. For example, if you were having an argument with someone, if you were pulled over for speeding--”

“I get the idea.”

“This is the setting I used...” He reversed the polarity of an important-looking switch. “Now, it can be directed toward someone else. Hence my idea of the highly marketable Revenge-O-matic 6000. You will finally get a pay-raise after the profits are well-reaped.”

“How much of a pay-raise?”

“There will be more on that subject later. First, let me tell you about my new invention.”

“I thought that's what we were doing.”

“The Blameter 6000 is an accessory, sold separately, and in effect, priced separately.”

“Okay, I'll bite. What does the Blameter do?”

“It allows the user, or customer, to blame his or her problems on someone else.”

“Is there a demand for that?”

“Demand will be created after Revenge-O-matics are in wide-spread use. The Blameter is a simple Revenge-O-matic detector. For example, if a friend, work colleague, or someone you love is accusing you of creating your own problems, the Blameter can be used to detect the nearest Revenge-O-matic that is being used against you. Once detected, you would simply show the Blameter LCD display to your accuser, thereby proving that someone else is responsible for your problems. If no Revenge-O-matic is detected, there's a small button underneath that when surreptitiously pressed, will trigger a false positive. In effect, you will be able to blame someone else for your problems, regardless of the truth.”

The Professor resumed speaking, but Nathan stopped listening, and had no feelings of guilt while completely ignoring Zinkerton. Nathan didn't want to distract him from his soliloquy.

He looked closely at an intriguing-looking control button. Underneath it was marked with fine print, very difficult to read, but Nathan, after a few seconds, managed to decipher it. The thought of using it made his nose twitch with delight and curious anticipation.

With the Professor's attention diverted by what the Professor was saying to himself, Nathan quietly and quickly pressed the button marked ‘erase from existence’.

“So Professor, what would happen if I pressed the execute button.”

The Professor stopped talking to himself, and replied to Nathan. “Nothing. The machine is still powered off.” Zinkerton turned the machine back on.

Nathan asked, “Now what would happen if I pressed the execute button?”

“Since I'm the person standing closest to you, my brain would be slightly disrupted and my fine motor control would lose its establishment.”

Zinkerton turned that feature off because he feared it. He turned on the feature marked ‘a rabid dog ate my homework, really it did’.

“Now it's safe. The only problem that will develop for me is that a rabid dog will eat my homework, of which I don't have any.”

Nathan smiled evilly at the Professor. “Zinkerton, you owe me a new computer, a new car, and possibly surgery to repair any unforeseen problems with my brain due to having its cells and fine motor control disrupted.”

“With the money we make from this machine... I mean the two machines, I'll be able to compensate you to the best of my satisfaction.”

“What's that mean?”

Professor Zinkerton waved his hand in front of Nathan's face as he said, “You serve me well, and you'll be rewarded.”

“Jedi mind tricks only work in the movies. Could you be more definite, Professor?”

“I am your father.”

“No, you're not. Do you plan on reimbursing me for the damage to my computer, my car, and my brain?”

“Why do you care so much about your brain? You should try meditation. Try letting go of attachment and accepting what is now.”

“Okay, Professor. That sounds fair. But before I accept the now, I have a button to press.”

He pressed the execute button. Nothing happened. Nathan frowned, then double-checked the fine print underneath the control button he'd set. “Erase from existence – twenty second delay.” Nathan waved goodbye. The Professor, who quickly figured out Nathan's diabolical plan, decided to smash the one-of-a-kind chip in the hopes of saving himself from being erased from existence. That last act doomed them both, leaving many alien races to wonder what had happened to the left side of the universe.