\chapter{The Five Alcoholics}

(ca. 1983)

Once upon a time there lived five alcoholics. The first alcoholic’s name was Flackenhap. He was a drunk driver. He was always in accidents. He was very poor because he had to pay for all the damages.

Since Flackenhap was always in an accident, he needed an agent. He was in so many accidents he needed his brother, the only agent he could find. His name was Tropplehop. He did good business because Flackenhap was always in an accident. He didn’t know how to shave his mustache and it grew one yard long. His beard was so long that when it touched the floor it went two feet in the air.

The third alcoholic was a member of the suicide committee. He was always trying to commit suicide. His name was Flackletap. Whenever Flackletap was trying to commit suicide, somebody stopped him.

The fourth alcoholic’s name was Nobody because he was fat and unemployed. His wife’s name was Framenheimer.

She drank so much it stunted her growth. She was only one foot tall.

One day Nobody asked Framenheimer “Do you want to have a child?”

Her reply was “Yes.” They drank so much it took 28 years. It was a girl. Her nose was upside down, she had three arms, one leg, and her name was Blacky the Kid.

Next month Flackletap was about to take pills when Nobody rushed in and said, “I want to put an end to Blacky the Kid because she is a girl.”

He grabbed the pills and put them into a piece of cake Blacky the Kid was eating. She swallowed the pills and asked, “Daddy, why you do dis to me?” Nobody became sad and he took the pills. Framenheimer became sad because Nobody died. She went outside and saw Flackletap about to jump off a cliff. She pushed him aside and she jumped off.

The next day Flackenhap was driving to the United States from Russia. When he was at the coast, a man in a limousine said to him, “I say my good fellow, if you don’t stop your car, you will fall in the ocean.” Flackenhap didn’t hear him because he drank so much. The beer went into his ears so he didn’t hear very good. He went in the ocean.

Next week Flackletap was going to jump in the water, when Tropplehop came and said, “Now that Flackenhap is gone, I’m out of business!” He jumped in.
Flackletap stared and said, “I lost my niece, my sister-in-law, and my three brothers. I don’t think I’ll try to commit suicide anymore!”