\chapter{Hovering on the Winds of Thought}

% Mentioned in the \chapter docs at
% file:///usr/share/texstudio/latex2e.html#g_t_005cchapter
%The paragraph that follows the chapter title is not indented, as is a standard typographical practice. To get an indent use the package indentfirst.

A lonely time ago, a space was hovering in the mist formed by the winds of thought. The space had no other purpose. One day, it realized it could do more than only hover, so decided to fly swiftly through the mist to find a purpose.

After an immeasurable amount of time, the space landed between some vowels. Although they didn't mind associating with the space, the new partners remained lost in a misty void and felt incoherent and incomplete. For many years they aimlessly floated through the darkness. Then one day, they lightly touched several confused consonants that were hovering upon a lazy breeze passing nearby.

Without warning, commas and periods began dripping from the sky. The space, the vowels, the consonants, the commas, and the periods delightfully joined together and soon gave birth to a healthy, well-formed sentence. It grew up to became a handsome, properly indented paragraph. Then the mist evaporated and gracefully waved goodbye to its former guests.

Fully developed chapters eagerly sprouted from the sentences and gently caressed all the characters that had joined together. As the chapters aged, a book lovingly wrapped around them, providing shelter from dangerous erasers, wet and fiery storms, and anything else that might disrupt their cohesion. A quickly-passing thought transformed into a title and rested upon the face of the book. The title found comfort upon its new bed and happily decided to remain.

Suddenly a strong wind grabbed the book and carried it from the void and into the hands of a smiling child. There was much time spent within the book, and the book was spent within time. It endured many storms and many thoughts.

Sadly, after hundreds of years, the book dissolved into a mist. Its characters were thoughtlessly scattered into a void.
\newpage
In the void, a lonely time later, there was a space.
\vspace*{\fill}

\centering
The Beginning
