\chapter{The Magic Brain}

Once upon a time, a man named Orson lived on the planet Aurelius. Orson had a wife, two children, and a very active imagination. At least once a day his family requested that he tell them a story or a joke. He gladly did so, creating events and characters so quickly that one would believe he was reading the story from a book, and his jokes were so funny that his children's cheeks were often sore from too much laughter.

Although interesting and imaginative, the characters in Orson's stories could not perform magic; they had no special powers nor could they grant wishes. The reason for this was that unlike the people of Earth, Orson, nor any other Aurelian, had ever encountered magical fairies or other cosmic beings who granted wishes or cast evil spells.

\timesep

On a bright, comfortably warm day, Orson sat on the grass, his back against a tree, looking at an extremely large rock. Although the rock was motionless and not doing anything noteworthy, Orson had been intently watching it for nearly two hours. This might seem like a boring activity to most people, but because he had a fluffy and glittery imagination, the things he saw on the rock were the same things the people of Earth would see on a movie screen. He was imagining an adventure unfolding, and with only the power of his mind, he was able to see many action scenes and characters joining together to form a movie.

Suddenly, a fairy appeared from a gentle wind blowing nearby. Most would think it impossible, but ze wasn't merely an \emph{imaginary} fairy—ze wasn't a fairy one might read about in \emph{fictitious} stories—ze was a \emph{real} fairy. Ze had white, translucent wings on zir back and was wearing an orange-colored casual suit that wrapped around zir tall and moderately plump body.

Orson had never before seen a fairy, so he had mixed feelings about zir sudden appearance. He was partly curious but also scared because he didn't know what a fairy was, nor what ze was capable of doing. Fortunately for him, ze was a good fairy."

“Hello," he said pleasantly. “My name is Orson.”

“Greetings, Orson. My name is Arden. I'm a good fairy. Consider yourself fortunate.”

He felt more relaxed after hearing Arden's pleasant-sounding voice and seeing zir friendly demeanor. Orson politely asked, “Would you like to sit with me and watch this interesting rock?”

“No, thank you. I've recently arrived on your world, and I'm here to grant you two wishes.”

“That sounds nice,” Orson said. "Which wishes would you like to give me?”

After a kind laugh, Arden replied, “I see you're not quite in tune with how this works. Allow me to elaborate for you—whatever you would like, no matter how impossible or improbable, I will give to you.”

“Okay, but I've never wished for anything before. Could I have some time to think about it?”

“Of course. Take all the time you need,” Arden replied congenially.

Orson considered several options and then finally decided. “I would like to wish for a magic brain. I would like a perfect brain that never makes mistakes.”

“Your wish is granted,” Arden said while dramatically waving zir magic wand. Instantly, all the colors of a rainbow streamed out of Orson's ears, nose, and mouth. He also became surrounded by the soft, upbeat music that is typically heard when a magic spell has been cast.

After a few seconds, the bright colors and twinkly music faded and vanished, which indicated the effect of the magic spell was complete.

Orson immediately noticed the difference in his brain. The thoughts in his mind seemed quieter and moved more slowly. He attempted to do a difficult math problem in his head—he thought, $128 \times 323 = ... 41,344$! And he knew with absolute certainty that he had calculated the correct answer.

He thanked Arden, and asked, “How may I contact you when I would like to fill my second wish?”

“Simply call out my name three times—the winds will carry your voice to me.” Ze then leapt upon a passing breeze and disappeared.

Orson sat down to continue watching the large rock, but failed to see anything interesting. Its surface was smooth but it also had a few sharp edges. He decided the rock no longer had any special features. Standing up, he departed for home.

\timesep

Orson lived in a three-room log cabin near the edge of a forest, in a village where eleven other families resided in cabins of their own. Between the village and the forest was a stream, which could be crossed using a narrow wooden bridge that had been built a decade before by Orson and three other villagers.

Orson was walking home through a large meadow on the opposite side of the village. Usually he greeted the cows and horses that were grazing in the meadow, but today he decided that saying hello to them was pointless.

He finally arrived home, and as he walked through the front door, his wife, Melody, and two children, Laura and Deborah, greeted him with happiness in their eyes and smiles on their faces.

“Hello, Melody. Hello, children.”

“Good evening, Father,” the children replied.

“Welcome home, Orson,” his wife said, giving him a kiss on the cheek.

“Why kiss me on the cheek? You've kissed me there many times already.”

Surprised and confused by Orson's reaction to her kiss, Melody thought he might be joking and studied her husband's face for a moment, but she was unable to detect any indication that he was playing with her.

Melody hesitated before replying, “I just—I just felt like kissing you.”

Orson thought for a moment, then simply said, “That sounds logical.”

Melody, still puzzled by Orson's odd behavior, didn't know what to say, but allowed the matter to rest for the present moment.

Melody resumed preparing dinner. The children became bored waiting for their meal and begged Orson to tell them a story.

He responded, “Okay. Give me a second to think of one.”

He tried to remember a story he once heard, but failed. He then attempted to invent one but he was unable to do that, too.

Melody, now recognizing with certainty that something was wrong with her husband, decided it was time to press for answers. “Are you feeling ill, Orson? You're acting very strange, and you never have difficulty thinking up stories to tell. Did something bad happen to you today?”

“Oh, no!” Orson replied. "Just the opposite, really. While watching my favorite rock, I was approached by a good fairy named Arden. Ze told me I could wish for anything I wanted.” Orson paused to take a sip of water, then continued. “I chose to wish for a magic brain—one that is perfect and incapable of making mistakes.”

The children laughed, and Laura exclaimed, “Father, that is a good story!”

Melody didn't have the same reaction though.

“Orson, that sounds impossible, but by the way you're acting I can't help but think you're telling me something true.”

“Yes, it is true.”

Melody thought for a moment, and decided to test him. “Orson, tell me a joke,” she ordered.

Orson's perfect brain went to work trying to think of a joke, but after a minute passed he gave up. Confusion and doubt settling in, he said, “I don't understand. My brain should be working better than before. It's supposed to be incapable of making mistakes. Perhaps Arden was really an evil fairy and lied to me!”

Melody cried, “No, Orson, you got your wish! Don't you see? Your brain can't make up a story or a joke because neither is based on perfect logic and facts. A perfect brain can't imagine things that aren't real, and it can't make a joke because most jokes are simply pure nonsense!” She sadly looked at her children, then back at Orson. “What shall we do now? The husband and father we knew is gone!” And her tears fell like streams upon her face.

Orson picked up a clean napkin from the table and wiped away her tears. “You are right of course, I'm certain of it. But don't worry, dear—Arden offered me two wishes, and I have one remaining!” Orson walked over to the window and called out, “Arden, Arden, Arden!”

With his words came the wind, whispering at first, then howling throughout the entire house. And Orson knew it was a magical wind because it disturbed nothing, and nothing was tipped over by its movement.

A gust of wind carried Arden inside. Ze hopped off to stand in front of Orson.

Smiling, ze said, “Hello again, Orson. Have you decided on a second wish?” The children stared at Arden with amazement and curiosity; Melody, however, glared with anger and wanted to yell at Arden.

Orson answered, “Yes, Arden. I've realized my brain worked better when it made mistakes. Please, I wish to have my imperfect brain returned to me.”

Arden understood and granted his wish, dramatically waving zir magic wand. Suddenly, colors and sparkling energy flew in from outside, through the windows and around all the objects in the kitchen, and finally streamed back into Orson's ears, nose, and mouth. He also became surrounded by the soft, upbeat music that is typically heard when a magic spell has been cast.

After a few seconds, the bright colors and twinkly music faded and vanished, which indicated the effect of the magic spell was complete.

Now that Orson was again himself, Melody forgave Arden and invited zir to dine with them. Afterward, Arden leapt upon a passing breeze, waved goodbye, and Orson and his family lived incorrectly ever after.