\chapter{Zachary's Brief Visit to the Other Side of the Wall}

Once upon a time, a young boy named Zachary was sitting at his kitchen table reading a book about an adventurous archaeologist. Wishing for an adventure of his own, he placed a bookmark inside and went to get a glass of orange juice from the refrigerator. After filling his glass, he sat back to continue his imaginary journey within the pages of the book.

Suddenly (as so often happens in a story such as this one you're currently reading), a magical thing happened to the wall behind him. It began to emit a slight creaking sound. Zachary turned around. Curious and confused, he examined the wall. The creaking became louder, and the wall began to shimmer and change color from beige to a bright, glowing gold. He walked backwards several feet, not afraid, mind you, but curious as to the intention of the wall and believed that stepping back for the moment might be a wise decision. The wall, not becoming any less boring really, ceased its noise-making, and became quite translucent.

Now the wall being clear made it far simpler to see what was on the other side. There was apparently a universe on the other side that was previously unknown to Zachary or his family (at least it was not mentioned in the purchase agreement when his parents bought the house). Now, stepping through a wall into another universe would be quite dangerous due to the lack of oxygen or ground upon which to walk. Fortunately for Zachary, who even at this moment was sipping his orange juice wondering if he was as interested in adventures as he previously thought, noticed a planet moving toward the wall.

Now a planet with atmosphere and ground seemed quite inviting and opened a new possibility which excluded death from a lack of oxygen and floating infinitely though a void in a universe located behind a wall in your parents home. As the planet became closer to the wall, a vast, sprawling civilization could be seen and soon a city was visible to little Zachary. He approached the wall slowly and attempted to touch it lightly with the tip of his forefinger. Imagine his surprise when his hand easily slipped through the wall. He now had a choice: continue drinking his orange juice and reading his book, or go through a magical wall to a planet in an as-yet undiscovered universe which held infinite possibilities for adventure and arousal. Setting his glass on the table and replacing his bookmark, he decided without much hesitation really, to step through the wall, while at the same time, conveniently forgetting to clean his room as his parents had asked him before they left for work.

Now, some logical grown-ups might recommend against stepping through a magical, translucent wall. Zachary, however, was not a logical, fact-filled grown-up, but a young boy who had never before been on a magic planet. The choice for him was quite simple really. So getting back to Zachary's place in the space-time continuum, he went through the wall and was now not in the city as one would necessarily like to be, but in the air above the city as one would be less likely for which to have a desire. Now as he was falling from the aforementioned air, he thought perhaps my orange juice and book would have sufficed. But as the choice was apparently no longer his to make, he quickly discovered that gravity here was quite similar really, to that of his own world. Now learning quickly that gravity would not help him, he tried to devise other modes of aid in his current predicament.

Fortunately for him, a hot-air balloon driver was nearby, and was able to maneuver his balloon into such a position that Zachary could land atop it. Air again became a friend to Zachary, and cushioned his fall atop the sturdy material which the balloon was constructed. The driver of the balloon made a hasty landing and once to the ground Zachary was safe once more, but did get a scrape on the knew when he got all the way down. The balloon driver queried the young man, “What is your name my flying fellow?”

“Zachary,” he replied.

“My name is Nathaniel. How did you come to be in the air above the city, in danger from gravity?”

“I was reading a book, and the wall in my kitchen became magical, and I saw this planet, and was bored, so I stepped through the wall.”

“Interesting,” the balloon driver replied. “And at any time had you given any thought as to how you would return home once you were done exploring our lovely universe?”

“Ummm... no. I don't normally think that far ahead. But that was my first magical wall, so...”

“I see. Well, what are you going to do now?”

“I'd like to have an adventure, sir, or go back home and read a book or take a nap.”

“Sir? Call me Nate. Well, the very least I can do is see if we can find a way back to your kitchen. Hop in the balloon.”

Zachary got in the balloon basket, and they took off. They reached the sky. There was a shimmering and Zachary reached his hand out. He was pulled in by the gravity from his home world, and scraped his elbow on a kitchen chair. His parents walked in the door.