\chapter{The Prisoner}

Look into the sky and you may see the Moon. If you look past it you'll see a bright star. Look past that star and open up your imagination. You'll see a distant, alien solar system. Within that solar system you'll see a moon. Stand upon that moon and you'll see a small world.

A prison is on that world, positioned miles underground where it's so dark even light is unable to travel. Living inside are people who have committed horrible crimes against their neighbors. They are locked into small cages surrounded by gray stone blocks cemented together.

One morning, a long time ago, one such prisoner was eating breakfast. A speck of light suddenly appeared several inches in front of zem. It momentarily hurt zirs eyes but the pain quickly subsided. Several seconds later the light changed from a speck to the same size as one of the blocks in the wall.

Ze was frightened by the light, but because ze was normally so very bored during his imprisonment, ze welcomed his fear, deciding it was an exciting change. Ze continued watching the light. The stone behind it slid slowly out of the wall and fell to the ground. It began to grow small arms, legs, a head; and finally, a mouth.

The mouth spoke, “Greetings, Inmate!”

“Uh... hello. What... who are you?”

“I'm a stone fairy.”

“Uh huh... okay. Are you a good stone fairy or an evil stone fairy?”

“That depends on you. I'm here to grant you one wish.”

For the prisoner, deciding on a wish was quite easy.

“I wish I were free from this prison.”

The stone fairy took a great breath and blew out small pebbles and dust, which filled the prison cell, swirled around the prisoner, and ze disappeared.

The prisoner was now upon the surface, where light could move about freely and the air was fresh and there was much space on all sides of zem. Ze was very happy to be free, and jumped into a nearby lake and swam about joyfully. After getting out of the water ze noticed something very strange—Ze was fourteen years younger.

The stone fairy suddenly reappeared.

“Good stone fairy, I made one wish, yet you have granted me two!”

“No, prisoner. I have only granted one wish. Because breaking you out of prison would have been illegal, I have sent you back into the past, to the point in time before you committed your acts of discourtesy and aggression against your neighbors.”

“Thank you, good fairy!” Then the fairy disappeared.

The prisoner started walking toward what used to be zirs home. When ze was only a few blocks away, ze had a choice to commit a crime, one which would give zem great pleasure. Unfortunately, ze proceeded to make the choice to commit an act of thievery. Along with the pleasure ze experienced, ze also had a sense of familiarity, and remembered this was the first crime ze ever committed.

Ze was instantly within a darkness through which even light could not travel. Ze walked into a wall and touched it with his left hand and felt a cold brick. Ze realized ze was back in zir prison. Ze cursed the stone fairy, and promised zirself to never again speak with an evil fairy.
