\chapter{The Camel in the Desert}

It was many years ago, on a planet in the Andromeda system, in a desert that spanned thousands of miles, when a furry brown camel walked near a narrow stream of water. He excitedly lowered his head to drink. Sadly, by the time his lips almost touched the water, it evaporated. He began walking again to find more. He'd hoped to find a lake, but even a small river would make him happy.

Being thirsty made him sad, but he was also sad because he was the only camel remaining on that planet. His other camel friends had died; most from old age, some from physical disease, and two from suicide. Regrettably, he hadn't been able to say goodbye to all of them.

He walked along further. In the distance, he saw a scaly gray lizard that wasn't moving. The camel approached him slowly and asked, “Mr. Lizard, why aren't you moving?”

The lizard replied, “Oh, Mr. Camel, I'm so thirsty I can barely move my legs even a little. I'm conserving my energy until it rains.”

“But that may not be for months! You'd probably die before it rains. Let me help; I have water stored in my hump. I'll give you some.” The camel spit on the lizard's back, and onto the ground in front of him. He drank and soon felt much better.

“Now climb onto my back. You can rest until I find a small river, or hopefully, a large lake.”

“Thank you, \textit{thank you}, Mr. Camel!” The lizard slowly crawled onto the camel's foot, up his leg, around his stomach until he was resting comfortably upon the camel's back.

They traveled many miles. Several weeks later, they spotted a woodpecker with black and white wings and a tan belly. She was very thirsty. After exchanging routine social pleasantries, the camel gave her some water, just as he had done for the lizard. He then invited her to perch on his tail while he continued his search for water.

Finally, they saw a small patch of grass, and beyond the grass, some green bushes. Beyond them was a large lake. The three travelers—after going through such a life-threatening ordeal—were now good friends. They each drank from the lake and ate berries from the bush.

After their meal, they spent a few hours scavenging the area to gather materials needed to build a rudimentary shelter.

It rained later that evening, and they knew they'd chosen a fine spot in which to stay. Soon, other creatures wandering through the desert found their little settlement. They expanded it over time, and after a few years it became a well-populated city. Rain fell regularly, ensuring none of its citizens ever died of thirst. It became a tourist attraction to some space-faring camels that landed there by accident when their ship ran out of ion particles (a fuel that could be engineered using water and leaves from berry-bushes).