\chapter{Mount Solation}

Once upon a time, a man stood upon a mountain. He was almost completely alone; the clouds drifting and hovering nearby were his only companions. Because the mountaintop was so high, only some of them were above him, others were below, and some he could touch. They sometimes whispered to him stories about life, men, and women.

One day, the man decided to give names to all the clouds. After 100,000 years, naming all the clouds became tiresome for the man, so he decided to stop that activity. After 10,000 years of not naming clouds, he thought to name the raindrops that they produced. After 50,000 years, naming raindrops grew tiresome so he decided to stop that activity.

After 5,000 years had passed, he had the idea to give names to the grains of sand and dirt he saw on the mountain. After 25,000 years, this began to tire the man. He decided to quit naming all the grains of sand and dirt.

After 10,000 years of not giving names to anything, he again fell victim to boredom. The man thought to name the mountain upon which he was standing. He spent 20,000 years choosing a name. He finally decided to call it \textit{Mount Solation}. He was very satisfied with it and decided to rest. He was so exhausted that he slept for 5000 years.

When the man awoke, there was a woman standing next to him. The man was surprised; he had never before seen a woman, but had only heard about them from the clouds. She greeted him with a smile. "Hello. What's your name?"

The man's expression flushed with embarrassment. "I forgot to give myself a name. I am the man."

She laughed and smiled pleasantly. "There are \textit{many} men. Everyone has a name; you must have one, too."

The man replied, "You say everyone has a name, then I agree that I must have one, too. Unfortunately, if I ever had a name, I have forgotten it. What is \textit{your} name?"

"Theresa," the woman replied.

"May I have it?"

"Have what?" Theresa inquired.

"Your name," the man answered.

Theresa laughed and smiled pleasantly. "But if I give you my name, then I won't have one."

"I understand. Perhaps I will give myself a name. I have named many clouds, raindrops, grains of sand and dirt, and also this mountain. Giving a name to myself should be very simple."

"One should expect so," Theresa laughed and smiled pleasantly.

The man sat down on a small pile of leaves and began to think of a name for himself. After 20,000 years, he decided on a good name. He looked around to tell Theresa his new name, but couldn't find her. The man was disappointed that although he now had a name, he had nobody to ask him what his name was, nor anyone to call him by his given name. For 250,000 years he wondered how to solve his dilemma; he occasionally slept between thoughts. The man talked to the clouds often and asked their advice. Sadly, after 200,000 of those years had passed, the sky cleared and became blue with no clouds to keep him company. The man had been completely alone for 50,000 years.

At the end of that time, a solution entered into the mind of the man. \textit{Today I will go down to the bottom of Mount Solation and look for Theresa.} The man began walking down his mountain.

He soon noticed the clouds had returned. He pondered about returning to the top of Mount Solation, but after a few seconds of thought, decided to continue downward.

For the first time, the man realized how high Mount Solation truly was. He  became amazed as he learned how high it stretched into the sky. He again reflected for a minute about returning to the top, but decided against it. He continued his slow descent.

Two days later, the man saw someone in the distance. He was quite surprised to see anyone, for he was still less than half-way from the top.

He recognized Theresa. Smiling, he yelled out to her, "Theresa!"

She responded, "Hello, man!"

They approached each other and the man said, "I've come to tell you my new name."

"That's wonderful! I'm glad you have a new name; I've been waiting for you to decide on one. Many times I've gone to the top of your mountain, but found you sleeping. I'd have come more often, and perhaps found you awake, but it's a very long walk up and down your mountain, and it uses up much of my time. Please tell me now, what's your name?"

"I have spent much time deciding on my new name. I could not tell you exactly how much though. Sometimes in the past, I have lost track of time. At one point, I thought to give names to the seconds which pass by me, but I was busy naming raindrops when that thought entered my mind. I had not the opportunity to name the seconds."

Theresa said, "That's all right. I don't want to know how much time or how many thoughts you spent choosing the name you've given yourself. I would just like to hear your name."

"Joseph," the man replied.

"I like that name. You've given yourself a fine name, Joseph."

"Thank you, Theresa. I came to find you so I could tell you my new name. Now that I have told you, I will go back up to the top of Mount Solation."

"Joseph, instead of going back to the top of your mountain, would you like to walk down to the bottom with me?"

"What is at the bottom of Mount Solation?"

"Many of the same things that are at the top: clouds, raindrops, and grains of sand and dirt. Also, I live at the bottom, and so do other men and women. There are many other things at the bottom of your mountain that aren't at the top."

"It sounds very much as what the clouds used to whisper to me. They used to tell me about life, men, and women."

Theresa said, "The clouds would know about all of those things. They've seen most everything. It was a cloud who whispered to me, and that's how I found you when we first met."

"Did the cloud tell you its name?"

"Yes. After it told me where to find you, the cloud told me its name was \textit{Theresa}."

"That is very interesting. I remember naming that cloud. It was the first cloud that ever whispered stories to me about life, men, and women. I named it \textit{Theresa}, and then it whispered to me that it knew another \textit{Theresa} and would tell her about me. Until now, I had forgotten about that whisper. I can't remember when it became lost from my mind, but I think it might have been while I was naming raindrops. I would like to find that cloud and thank it for keeping its promise."

"I'm sorry to say this, but you won't find that cloud. It transformed into some of the raindrops that you named. Parts of it now float through a river which passes along the bottom of your mountain, and carry along many of the grains of sand and dirt you've named."

Joseph frowned. "It saddens me about that cloud being gone."

"It's not gone—it still exists as the river, the riverbed, and is part of many other clouds that you now see.

"Many years ago—one of the times I went looking for you and found you sleeping—I almost died of thirst before I was able to return to the bottom. Fortunately, the river gave me some of its water and I continued to live."

After a moment's pause, Joseph said, "The bottom sounds like a good place to be. Thank you for suggesting it."

They started walking downward. Much of the time was spent talking. When they finally arrived at the bottom, they were very thirsty. Fortunately, the river was overflowing and able to provide them with the water they needed.

Joseph and Theresa visited each other frequently during the many years that followed, along with the many other people at the bottom of Mount Solation. Ever after, Joseph lived, and experienced that which the clouds had whispered about to him, once upon a time.