\chapter{The Blind Man and His Neighbors}

A kind, gentle man and his family once lived in a large forest. His family and friends all loved him, and agreed he loved God and wanted always to do the right thing. He was even good to the animals who lived nearby. He was poor but had enough money to make sure his family remained fed and healthy. Despite his lack of wealth, he kept a positive attitude and his face nearly always held a friendly smile.

There were citizens in a neighboring town, however, for whom the man held no good feelings. They had a bad reputation and dressed strangely, and spoke oddly. Outwardly he wasn't mean or disrespectful to them; but he avoided and ignored them, and tried pretending they didn't exist.

One day the man was in the forest chopping wood to heat his home, and provide his good wife with fuel for cooking. As he chopped, small wood chips suddenly flew into his eyes. They penetrated deeply and swiftly. He screamed with agony. His wife came running. Upon seeing the pain on her husband's face and that he was using his hands to cover his eyes, she realized immediately what had happened. She quickly grabbed him and entered their vehicle, and drove him to a nearby hospital. When they arrived he was soon taken to an emergency room, diagnosed, and operated on. Finally the man's eyes were bandaged. He was then wheeled to a recovery room and tucked into a nice, comfortable bed.

He had no extra money with which to pay for his treatment. Because he was a poor man with a family to support, the hospital staff told him that after he was well-recovered he could settle his bill by performing volunteer work. He thanked them, and thought, “The people here are good souls. They must have great love for God, and will earn a place in Heaven.”

By how they spoke and acted, he knew they were the people with whom he was familiar. He was positive their skin was the same color as his own, that their eyes were the same shape as his, and that they were of a proper height.

A doctor came into the room where the man was recovering. He said, “Your eyes had quite a shock but they'll be fine. In time, you'll see just as well as before--maybe even better.”

“That's great news, Doctor. You've done such a good job, and seem very competent and well-educated. You are certainly one of God's creatures.”

“Thank you, sir,” the doctor pleasantly acknowledged.

“And the nurses here are very good, too. They seem well-trained and able to communicate with the patients quite well. They're very compassionate and understanding. They must have been raised in good and decent families.”

The doctor smiled and said, “I'll pass along your high praises to them. I have to visit some other patients now. Rest easy and may God bless you and your family.”

“And you as well, Doctor.”

The doctor left, and the man's family entered. They were overjoyed to hear that his sight would return. They visited everyday and brought fresh food from their garden to give to the hospital staff.

Several months passed and finally the man's bandages could be removed. The doctor was in the room and also a nurse, ready to assist. Another person was cleaning the room, making sure that patients didn't get infections and always had clean sheets and a clean bathroom to use. The family was waiting outside.

The doctor slowly and carefully removed the bandages. The man blinked several times so his eyes could get adjusted to the light. Finally he was able to see the doctor, the nurse, and the person cleaning the room. The man was absolutely astonished at what he saw! The doctor's skin color was different than his own! The shape of the nurse's eyes was not the same as his own! The height of the person cleaning the room differed by several inches!

The man quickly realized that his wife--in her panic--had taken him to the hospital in the strange town because it was the closest. He was grateful, and now knew he'd been using his eyes, not his heart, to judge people. As the doctor had predicted, his sight was better than before the accident. The man thanked God for the opportunity to learn an invaluable lesson about his neighbors on the Earth. From then on, he opened his heart and closed his eyes to see people for whom they truly were.