\chapter{The Search for the Enchanted Balls}
\setlength{\parindent}{2em}
% \fontsize{16pt}{16.3pt}
\Large
\baselineskip=1.15\baselineskip

% Doesn't work, fonts substituted
%\fontfamily{FreeSans}
% \renewcommand{\baselinestretch}{1.00}\selectfont
% \renewcommand{\familydefault}{GNU Freefont Sans}

% Proper nouns should not be hyphenated
% http://theworldsgreatestbook.com/book-design-basics-hyphens-justification/
%\hyphenation{
%	Kath-a-rine
%	Ja-cob
%}


Once upon a time, on a world similar to our own yet very far away, there existed strange animals who roamed carefree over its unspoiled landscape. They lived in harmony with their neighbors and gathered regularly for the purposes of frolicking and celebrating special occasions. In summer, they would picnic near the beaches of lakes that were so clean that all the life that swam within it was clearly visible. They played joyfully in vast, grassy fields. It was quite common for the animals of this world to live for thousands of years.

Two cats were members of this community: Katharine, a primarily orange cat with narrow brown stripes; and Jacob, who had black fur on his back that blended into gray around his sides and white near his tummy. They had been best friends for many hundreds of years. They played with their enchanted balls almost every time they got together. Katharine's ball was pink with purple stripes. Jacob's was bright green with small yellow circles.

Almost every day they played in a meadow covered with green grass and dotted with yellow and red wildflowers. When the grass grew too high, several helpful sheep would eat some. The cats were grateful for the sheep’s efforts - Katharine and Jacob found it much easier to play with their enchanted balls when they could see each other, and their balls could move freely over the ground.

One day as they were playing, they both became distracted by a large dog wandering nearby. They turned their attention back to their enchanted balls, but to their dismay, the balls had vanished from sight. They frantically searched the field for several hours. When the sun set, however, they reluctantly agreed to return to their homes for the night and continue their search tomorrow. They were heartbroken. After arriving home, Katharine and Jacob fell into their beds, all joy and hope drained from their bodies. They cried and meowed until a heavy sleep overtook them.

After only a few hours, their sleep became disturbed by nightmares and their limbs twitched frequently. When they were awakened by a rooster crowing at the rising sun, they were relieved, but felt as if they hadn't slept at all. Later that morning, Katharine and Jacob met under a weeping willow tree standing near a lakeshore. They peered out over the water, which softly reflected the sunlight. Neither of them appreciated or even noticed the beauty of the scene, nor of the shade and shelter the tree generously provided to them.

Both their tails hung low. Katharine suddenly turned to look at Jacob. As they stood there, Jacob saw that Katharine was thinking hard, and then he observed her tail slowly begin to rise. Katharine declared, “We have to keep searching.” Jacob sadly looked into her eyes. She continued, her voice firm and direct. “It doesn't matter how much time we spend; at any cost, we have to find them.”

Hesitantly, Jacob replied, “We looked all over that field. We covered every square inch. Where else could they be?”

With a wry smile, she answered, “We'll know that when we find them.”

Jacob looked dubious but after a few moments he finally agreed. That fateful day, they both completely committed themselves to the search for their enchanted balls.



ttttttt



Katharine and Jacob left to travel the world to search for their beloved toys. They didn't know how long their search would last or how far they would have to travel to find their precious treasures, but they were determined.

Several decades after their search began, humans came to the world and began colonization. Steamships and airplanes were among the many things the newcomers constructed. Katharine and Jacob took advantage; they were able to stow away on vehicles that traveled across the lakes and through the sky, which allowed them to search areas they hadn't been able to reach before.

After many years they managed to completely search their entire world but still they hadn't found their balls.

It was around that time when the humans began building spaceships. Katharine and Jacob curiously watched their construction. They ran away in fear the first time they heard one launch. Later, they crept into a large building near the launchpad and eavesdropped on conversations of the ground crew flight coordinators. The cats happily learned that spaceships could help them continue their search. One night, they sneaked into a top-secret facility, sniffed the area, and spotted some very large plastic cargo containers. They jumped up and landed inside one. Most of their weight fell against the side and it almost tipped over. They landed on human clothes and blankets. They burrowed under the soft, warm material.

After only a few minutes they heard a human walking nearby. Then they heard a “snap” as a lid was secured over the crate.

“Kat, I'm starting to wonder if we're making the best life-choices.”, Jacob declared.

“Keep quiet. We'll be all right. Did you sharpen your claws yesterday?”

“Yes. Do you think we'll have to resort to violence?”

“Probably not.” Katharine replied in a flat tone that didn't sound convincing or reassuring to him.

They felt the container being picked up, moved a few feet and set down on a wheeled cart. It was pushed to the launchpad and someone carried the container into a ship's cargo hold.

They didn't know what fate had in store for them, but decided to keep waiting.

They pushed up on the container's lid. It didn't budge. They continued trying for two minutes. They looked around for a tool and found a belt buckle. They were able to wedge open the lid enough to loosen it. Now, they were confident that escape at the last minute was possible, if they felt it was too risky to proceed.

Suddenly, the ship's engines came to life, making a sound more powerful than either Katharine or Jacob had ever heard before. They got scared but made sure not to loudly meow or cry. Their tails became very tense, but they stood their ground, refusing to allow this opportunity to find their balls slip from their grasp. %FIXME



ttttttt



Two days passed; the spaceship hadn't yet landed, but Katharine and Jacob were starving and thirsty. They agreed they'd better search for a food and water supply, so Jacob opened the lid far enough to get out. From being loosened by the belt buckle, it separated easily from the top of the container. They both crawled out and then stretched their bodies and tails as much as possible. They had never been trapped for two consecutive days but agreed it would be worth it to find their balls.

Katharine and Jacob sniffed around, whiskers twitching wildly. After several minutes they found a water source and scraps of food left by some crew and passengers (who apparently didn't understand that food is meant to be eaten, not thrown onto the floor). Katharine and Jacob easily found enough food and water to satisfy their appetites.

They desperately needed to use the bathroom before going back to their container. Fortunately, they had observed the humans using a computer-automated waste recycling system, and were able to dispose of that which they would have otherwise buried in sand or dirt. Afterward, they went back to the container and slid the lid back into place. They fell asleep in only a few minutes, and blissful dreams about their enchanted balls began shortly after.



ttttttt


% food and water = sustanance?
After three months of confinement interspersed with scrounging for food and water, Katharine and Jacob felt the spaceship land. They were in good health but poor spirits; they cheered up considerably when they knew the ship was on the ground and their freedom was imminent.

Jacob whispered, “How long should we wait?”

“After the human voices and footsteps disappear. We'll watch carefully and try to follow the last one outside.”

Katharine and Jacob knew how many people had originally boarded the ship; they had figured it out easily during their three months on board. They also knew one had died en route; a passenger had contracted some disease that wasn't detected before departure. Without proper medical facilities or treatment available on the ship, “There wasn't anything that could be done,” the Captain was heard to state, with regret and sadness clouding his voice. The passenger was given a respectful funeral, and ejected into space. The gravity from a star pulled her in, and was therefore cremated. According to her will, that was the custom in her family.

Katharine and Jacob counted the humans as they left the ship. One of them had a frayed thread hanging from his shirt. Jacob wanted to chew on it and bat it with his paw, but Katharine held him back. She snapped,  “Jacob, remember why we're here!”

Katharine counted the humans as they exited the ship. “16...17...18...19. All right, quietly now, let's get behind that tall human and follow him out; he's the last one. As soon as we're on the other side of the doorway, look for cover, and then run toward it as fast you can.”

They sneaked over to the human's feet, Katharine on the left, Jacob on the right. The human suddenly stopped, put his arm to his face and sneezed. The cats looked at each other with concern. They had heard humans do this before and knew that sneezes sometimes happened when humans were in proximity to cats.

He pulled a handkerchief from his pocket, blew and wiped his nose; then he glanced down and spotted Katharine and Jacob. They looked directly into his eyes but weren't able to sense whether danger was imminent. Jacob looked to Katharine for guidance. Trying to scare the human, she meowed loudly, bared her teeth and emitted a hissing sound. Her efforts were in vain. The human simply turned his head and shouted outside, “Captain! We got stowaways!”

He leaned over, hands coming down in Jacob's direction. “Run, Jacob!” Katharine commanded, her instincts taking over. Jacob sprinted toward the doorway. Katharine followed him straightaway.

They got past the exit and kept running in a straight line, darting past five humans easily; however, one was standing directly in front of their escape route. It was the ship's captain, and he looked very displeased. He squatted downward to snatch Katharine and Jacob. Katharine directed Jacob, “Veer left! I saw some thick bushes!”

Jacob hadn't seen any but he trusted Katharine enough to do as he was told. He slowed almost to a stop and started to make the turn, but the captain grabbed him by the sides of his stomach and scooped him up. “Well, little fellow, did you think you could get free passage on my ship and then just run away like a scared little kitty-cat?” Jacob squirmed in his grasp, squealed loudly, then looked to his left. He saw a bunch of green raspberry bushes but didn't see Katharine anywhere. \textit{I hope she got away}, thought Jacob.

“Argh!” the captain suddenly cried out, dropping Jacob.

He landed safely on his feet and saw Katharine gripping the captain's right leg with all four paws. Jacob realized she had created a diversion by digging her claws deeply into his calf. The captain bent over to reach for her. At the same moment, she retracted her claws, fell off the captain's leg, and yelled, “Run to the bushes, Jacob!”

Jacob ran as fast as he could. Halfway to the bushes, he looked behind to make sure Katharine was with him. He saw the captain running after her, but she was far enough ahead of her pursuer that her safety was guaranteed, as she'd easily outrun him. %FIXME

He reached the bushes, ran behind them, and then zig-zagged through some tall flowers. He stopped to wait for Katharine. Katharine, familiar with his smell, found him easily. They heard the captain and two of his crew members nearby and swiftly approaching. “There, that forest.” Katharine pointed to a large wooded area. “But there's no cover between here and the edge of those trees! They'll catch us!”

“We can outrun them. Let's go.” Katharine started to sprint towards the tree line, not waiting for him to verbalize his agreement. Jacob decided there was no other choice and continued after her.

After two minutes of chasing Katharine and Jacob, their pursuers stopped. The captain, giving up the search, shouted after them, “If I ever see you two again you won't be as lucky! From now on, I'll make sure there's a dog on every ship to prevent stowaways like you from ever boarding!” The captain and his two crew members walked back to the ship, feeling angry and humiliated after being outsmarted by two cats.



ttttttt



Katharine and Jacob reached the tree line, and entered the forest. After walking for several meters, they stopped at a large, soft pile of leaves and crawled on top. They lay down to rest for several minutes. Then Jacob said, “We'll never be able to get back home.”

“Let's not worry about that now. At least we're safe now–and we still have to find our balls.”

“What makes you think they're even on this world?”

Suddenly, Katharine and Jacob heard pawsteps coming from several meters away. They looked in the direction of the sound and saw a white Persian cat approaching. He didn't have a fighting posture, but Katharine and Jacob remained cautious.

The Persian cat stopped walking and sat down on his hind legs. He said, “I understand you are searching for something. Often when one stops looking is the time when he can truly see.”

Katharine and Jacob looked at each other, a question on their face. Katharine asked, “Who are you?”

“My name is Tobias. And you?”

“I'm Katharine, and this is my friend, Jacob.”

“It is a pleasure to meet you. Welcome to the forest.”

“Thank you,” Jacob replied. “Is this your home?”

“My home is anywhere I am happy and content.” Tobias paused, closed his eyes, took a deep breath, and exhaled. “I overheard you speaking about the search for your balls. May I ask why?”

Katharine replied, “They were enchanted, and before we lost them, they were our favorite toys.” Katharine told Tobias the story of their search; Jacob filled in a few of the gaps he believed relevant.

After they had finished their tale, Tobias said, “It is unfortunate that you lost your enchanted balls, but in my opinion, it is even more unfortunate that you've wasted so much time looking for them.”

Katharine and Jacob became angry and reflexively extended their front claws. Jacob said, “It wasn't a waste! We just haven't found them yet!”

Katharine said, “You don't understand. You never played with our balls and so don't realized how important they were.”

“Forgive me. I did not mean any offense, nor did I intend to minimize your efforts or grief.” Tobias paused, closed his eyes, took a deep breath, and exhaled. “Have you considered the possibility that your enchanted balls rolled into a lake and became submerged?”

Katharine retracted her claws, and replied, “Yes, of course. But Jacob and I don't like water. It's all right to drink but other than that I don't really see any purpose to water.”

Jacob continued, “We stayed on dry land most of the search. There were times we stowed away on boats to search other areas of dry land, but we didn't really care for the water being on all sides of us. It was really very nerve-wracking.”

“I see,” said Tobias. He paused, closed his eyes, took a deep breath, and exhaled.

Katharine asked, “Why do you keep doing that?”

“It relaxes me.”

“Are you nervous?”

“No,” he answered. “Deep breathing is a habit I started a long time ago. It helped me through a very difficult period in my life.”

“What do you mean?” Jacob inquired.

“One day, many years ago, I had a friend named Brittany. She and I were playing with our enchanted balls. We lost control of them, watching helplessly as they rolled into a fast-moving river. We ran along the riverbank after them, seeing them floating on top but powerless to do anything about it. They river kept carrying them further away—it became clearly evident that we would not be able to retrieve them.

“Suddenly, Brittany said, 'I'm going in.' I tried to stop her. As she was about to jump in, I shouted after her, 'No, Brittany! It's water! You'll never survive!' Disregarding my warning, she jumped in.” Tobias paused, closed his eyes, took a deep breath, and exhaled.

“I never saw her again. I believe she now rests with the Divine Felinity, in the spiritual realm where food is always abundant and cats never gain weight; where water never touches a cat's fur but is always cool and refreshing to drink; the place where there is a new toy every day and one's curiosity is always stimulated by some external object with a new smell.

“Although she's at peace, I do still miss her.”

“That's awful!”

Jacob looked thoughtful. “I almost lost Katharine during our search when she was captured by a human.”

“I hope you consider yourself fortunate.”

“Yes. But we still need to find our balls.” Katharine declared.

Jacob paused, closed his eyes, took a deep, and exhaled. “Katharine, no, we don't.”

“Jacob? What are you saying?”

“Our search nearly cost you your life. You mean more to me than any enchanted ball.”

“But Jacob, we made a pact!“

“Katharine, you're a good leader, good at making instant decisions—but take a minute to think of how you'd feel if, during our search, you lost me.”

Katharine didn't need a minute. After a few seconds, she knew her friend was correct.

Tobias said, “Come my friends. This forest has much to offer. There is much food, many new things to smell, and it offers an abundance of corners and things which you may hide under, if you feel the need. I believe you will find peace and contentment if you decide to stay.”

“Thank you, Tobias.”

“Some even say this forest is enchanted.”

Indeed, Jacob looked around and spotted some low-hanging vines swaying in the breeze and exclaimed, “\textit{Those} look interesting!”