\pagestyle{fancy}
\fancyhead[L,C,R]{}
\setlength{\headheight}{15pt}
\fancyhead[RO]{Mental Dimensions{\hspace{2em}}{∞}{\hspace{2em}}{\thepage}}
\fancyhead[LE]{{\thepage}{\hspace{2em}}{∞}{\hspace{2em}}Andrew G. Alt}
%\renewcommand{\headrulewidth}{0.4pt}

\chapter{Hovering on the Winds of Thought}
\setlength{\parindent}{2em}
\Large
\baselineskip=1.15\baselineskip

A lonely time ago, a \textit{space} was hovering in the mist formed by the winds of thought. The \textit{space} had no other purpose. One day, it realized it could do more than only hover, so decided to fly swiftly through the mist to find a purpose.

After an immeasurable amount of time, the \textit{space} landed between some vowels. Although they didn't mind associating with the \textit{space}, the new partners remained lost in a misty void and felt incoherent and incomplete. For many years they aimlessly floated through the darkness. Then one day, they lightly touched several confused consonants that were hovering upon a lazy breeze passing nearby.

Without warning, \textit{commas} and \textit{periods} began dripping from the sky. The \textit{space}, the vowels, the consonants, the \textit{commas}, and the \textit{periods} delightfully joined together and soon gave birth to a healthy, well-formed sentence. It grew up to became a handsome, properly indented paragraph. Then the mist evaporated and gracefully waved goodbye to its former guests.

Fully developed chapters eagerly sprouted from the sentences and gently caressed all the characters that had joined together. As the chapters aged, a book lovingly wrapped around them, providing] shelter from dangerous erasers, wet and fiery storms, and anything else that might disrupt their cohesion. A quickly-passing thought transformed into a title and rested upon the face of the book. The title found comfort upon its new bed and happily decided to remain.

Suddenly a strong wind grabbed the book and carried it from the void and into the hands of a smiling child. There was much time spent within the book, and the book was spent within time. It endured many storms and many thoughts.

Sadly, after many years, the book dissolved into a mist. Its characters were thoughtlessly scattered into a void.
\newpage
In the void, a lonely time later, there was a \textit{space}.
