\chapter{The Prisoner}

Look into the sky and you may see the Moon. If you look past it you'll see a bright star. Look past that star and open up your imagination. You'll see a solar system. Within that solar system you'll see a moon. Stand upon that moon and you'll see a small world.

There is a prison on that world, positioned miles underground where it's so dark even light is unable to travel. Living inside are people who have committed horrible crimes against their neighbors. The prisoners are locked into small cages surrounded by gray stone blocks cemented together.

One morning, a long time ago, a prisoner was eating breakfast. On the wall in front of him appeared a small pinpoint of light. It momentarily hurt his eyes, but the pain quickly subsided. Several seconds later the light grew bigger until its size matched a gray stone block.

The prisoner was frightened but because he was so very bored much of the time, decided to keep watching the light to see what it would do next. The stone behind the light slid slowly out of the wall. It fell to the ground. It began to grow small arms and legs and a head. A small mouth formed on the head.

The mouth spoke, “Greetings, Inmate!”

“Uh... hello. What... who are you?”

“I'm a stone fairy.”

“Uh huh... okay. Are you a good stone fairy or an evil stone fairy?”

“That depends on you. I'm here to grant you one wish.”

For the prisoner, deciding on a wish was quite easy.

“I wish I were free from this prison.”

The stone fairy took a great breath and blew out small pebbles and dust, which filled the prison cell, swirled around the prisoner, and he disappeared.

The prisoner was now upon the surface, where light could move about freely and the air was fresh and there was much space on all sides of him. He was very happy that he was free, and he jumped into a nearby lake and swam about joyfully. It wasn't until after he got out of the water when he noticed something very strange. He was fourteen years younger.

The stone fairy suddenly reappeared.

“Good stone fairy, I made one wish, yet you have granted me two!”

“No, prisoner. I have only granted one wish. Because breaking you out of prison would have been illegal, I have sent you back into the past, to the point in time before you committed your acts of discourtesy and aggression against your neighbors.”

“Thank you, good fairy!” Then the fairy disappeared.

The prisoner started walking toward what used to be his home. When he was only a few blocks away, he had a choice to commit a crime, one which would give him great pleasure. Unfortunately, he proceeded to make the choice to commit an act of thievery. Along with the pleasure he experienced, he also had a sense of familiarity, and remembered this was the first crime he ever committed.

He was instantly within a darkness through which even light could not travel. He walked into a wall. He touched it with his left hand and felt a cold brick. He realized he was back in his prison. He cursed the stone fairy, and promised himself to never again speak with an evil fairy.